MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-09-10 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}.

@@

\subsubsection{filtered data}\label{sss:filtereddata}

>>>>

@@

\subsubsection{filtered data}\label{sss:filtereddata}
We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}. The raw data provides real-world QoS evaluation results from several users on 5,825 Web services over 64 different time frames\footnote{http://www.wsdream.net/}. In this data set, each web service is associated with a number of features that reflect its functionality. By summarizing the data provided for each web service over different time slots, we have acquired three quality feature for each individual web service. There quality features are the three internal features introduced in section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}. To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services. Therefore, we have generated an array of web services with 5 distinct features.
